The K2 Bright Star Survey

### 2019-05-06 paper/ms.tex
farr and hogg on author list

@@

We would like to thank Will Farr for his very helpful comments on the halo method.

>>>>

\author[0000-0003-1540-8562]{Will M. Farr}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
\affiliation{Department of Physics and Astronomy, Stony Brook University, Stony Brook, NY 11794, USA}

\author[0000-0003-2866-9403]{David W. Hogg}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
\affiliation{Max-Planck-Institut f\"{u}r Astronomie, K\"{o}nigstuhl 17, D-69117 Heidelberg}
\affiliation{Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

@@
